---
title: "Stats_Group_Example"
author: "Patrick Daniele"
date: "December 3, 2018"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Prepare for analyses
```{r}
set.seed(1234)
library(ggplot2)
library(lattice)
```


## Basic console output
To insert an R code chunk, you can type it manually or just press `Chunks - Insert chunks` or use the shortcut key. This will produce the following code chunk:

    ```{r}
    
    ```

Pressing tab when inside the braces will bring up code chunk options.

The following R code chunk labelled `basicconsole` is as follows:

    ```{r }
    x <- 1:10
    y <- round(rnorm(10, x, 1), 2)
    df <- data.frame(x, y)
    df
    ```
    
The code chunk input and output is then displayed as follows:

```{r basicconsole}
x <- 1:10
y <- round(rnorm(10, x, 1), 2)
df <- data.frame(x, y)
df
```

## Plots
Images generated by `knitr` are saved in a figures folder. However, they also appear to be represented in the HTML output using a [data URI scheme]( http://en.wikipedia.org/wiki/Data_URI_scheme). This means that you can paste the HTML into a blog post or discussion forum and you don't have to worry about finding a place to store the images; they're embedded in the HTML.

### Simple plot
Here is a basic plot using base graphics:

    ```{r }
    plot(x)
    ```

```{r simpleplot}
plot(x)
```